% Awesome Source CV LaTeX Template
%
% This template is originally maintained by Christophe ROGER from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% This modification has been download from:
% https://github.com/innerTide/awesome-neue-latex-cv-extended
% Author:
% Yuefeng Wu
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
% Section: Projects
% Usage: 
% \project
%  {<End date>}      {<Project Title>}
%  {<Start date}     {
%                      <Contribution to the project>
%                    }
%                    {<Technology list>}
%
%


\sectionTitle{Projects}{\faCode}
\begin{projects}
  
  
  \project
    {Jan. 2017}   {IoT Broker of Smart Office Lighting System}
    {Nov. 2016} {
                      \begin{itemize}
                        \item The course project of Internet of Things.
                        \item Designed the architecture of the broker.
                        \item Implemented the app on Android for users to control lights.  
                        \item Implemented the broker’s HTTP interfaces to the building manager's server and the user app.
                        \item Integrated external applications, e.g. Avahi, Leshan, to the broker's program.
                        \item Co-debugged the program with the other group working on the server application.           
                      \end{itemize}
                    }
                    {Java, Linux, Android, IntelliJ Idea, Maven, GSON, MongoDB, Leshan (LWM2M), Avahi (mDNS/DNS-SD), Mosquitto (MQTT), VirtualBox, HTTP Protocol, Git}
  \emptySeparator
  
  
  \project
    {Sept. 2016} {Design of Dynamic Channel Selection Mechanism}
    {Nov. 2016}    {
                      \begin{itemize}
                        \item The course project of Networked Embedded Systems.
                        \item Designed and implemented the mechanism for IEEE 802.15.4 on Contiki OS. 
                        \item Simulated the mechanism with Cooja Simulator and analysed the results.
                        \item Composed the project report in academic English.
                      \end{itemize}
                    }
                    {C++, ContikiOS, Cooja, IEEE 802.15.4, Git, \LaTeX}
  \emptySeparator
  
  
  \project
    {Apr. 2016}     {Social-Networking App Based on Bluetooth Tags}
    {}    {
                      \begin{itemize}
                       \item A solution to the Fashathon held by Future Fashion to provide a creative method for social networking.
                       \item Designed the initial idea based on the challenges and supplied components with the teammates.
						\item Developed an Android app for demonstration in half a day.
                      \end{itemize}
                    }
                    {Java, Android, Android Studio, Bluetooth}
  \emptySeparator
  
  
  \project
  {Mar. 2016}       {Digital Image Processing Application on Multiprocessor Platform}
  {Feb. 2016}      {
                      \begin{itemize}
                       \item Laboratory work of Embedded Software.
						\item Implemented gray-scale and edge detection algorithms on a penta-core platform.
						\item Optimised the code and achieved the highest throughput in the class (almost three times as much as the passing standard).
                      \end{itemize}
                    }
                    {C++, $\mu$C/OS-II, NIOS-II, Multi-core Programming, Real-time System, Git, \LaTeX, Eclipse}
  \emptySeparator
  
  \project
  {Sept. 2015}		{Eye-Protection Application Based on Tobii EyeX}
  {}				{\begin{itemize}
  						\item A solution to a weekend hackathon to assist users to maintain correct reading posture.
						\item Implemented the demo application with Visual C++ in one day.
  					\end{itemize} 
                    }
                    {Visual C++, Tobii SDK, Visual Studio}
\emptySeparator


  \project
  {June 2015}		{Bachelor's Thesis: Security Mechanism Design for Wireless Networks and IoT Systems}
  {Dec. 2014}		{\begin{itemize}
  						\item Designed an authentication mechanism for wireless networks of IoT and mobile devices.
						\item Implemented the mechanism demo with Android devices and CC2530 ZigBee modules.
                        \item Awarded excellent graduation thesis.
  					\end{itemize} 
                    }
                    {C, Java, Android, NFC, Wi-Fi, ZigBee, Eclipse}
\emptySeparator


\project
  {May 2015}		{User Identity Authentication and Exchange System}
  {Apr. 2014}		{\begin{itemize}
  						\item A system to transfer the authenticated user identity to another device via a secured NFC connection.
						\item Implemented face detection and verification with cloud computing API (Face++).
                        \item Designed and implemented a secured data exchange mechanism based NFC connection.
  						\item Funded by National Student Innovation Training Program (STITP). 
  					\end{itemize} 
                    }
                    {Java, Android, NFC, HTTP, Face++ API, Eclipse}
\emptySeparator

\project
  {May 2015}		{Military Goose Step Evaluation System}
  {Apr. 2014}		{\begin{itemize}
  						\item A system to measure and grade orderliness of the goose steps of different squares objectively. 
						\item Designed the evaluation algorithm and implemented the system with NI LabView.
                        \item Awarded the first prize in 13th Challenge Cup of Tianjin.
                        \item Covered by several mainstream media in China.
  					\end{itemize} 
                    }
                    {NI LabView, Signal Processing, Wavelet Noise Reduction}


\end{projects}

